MINOS Handover Plots

### 2023-05-16 minos/validation/cross_validation.Rmd
Changed order of modules in the cross_validation.yaml file (probably doesnt matter but did it anyway). Added another plot to the cross_validation Rmd script just showing box plots of hh_income with no min max subsetting (did that in another plot as the outliers dominate the plot if not)
Renamed all instances of SF_12 to SF_12_MCS, and added the SF_12_PCS variable. Also created a PCS module, and tried to modify the outcome visualisation stuff but made some mistakes so still WIP. Handovers work, but cross-validation also still has some issues

## SF12

```{r}
sf12.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'SF_12')

plot_mean_comparison(pivoted.df = sf12.pivoted, 
                     var = 'SF_12', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

compare_boxplot_long(pivoted.df = sf12.pivoted,
                     var = 'SF_12',
                     scen1 = 'raw',
                     scen2 = 'simulation')
```

@@

```{r}
sf12.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'hh_income')
sf12.t.tests
```

```{r}
yearly_box_plots(pivoted.df = sf12.pivoted,
                 var = 'SF_12',
                 scen1 = 'raw',
                 scen2 = 'simulation')
```

>>>>

## SF12_MCS

```{r}
sf12.m.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'SF_12_MCS')

plot_mean_comparison(pivoted.df = sf12.m.pivoted, 
                     var = 'SF_12_MCS', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

compare_boxplot_long(pivoted.df = sf12.m.pivoted,
                     var = 'SF_12_MCS',
                     scen1 = 'raw',
                     scen2 = 'simulation')
```

@@

```{r}
sf12.m.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'SF_12_MCS')
sf12.m.t.tests
```

```{r}
yearly_box_plots(pivoted.df = sf12.m.pivoted,
                 var = 'SF_12_MCS',
                 scen1 = 'raw',
                 scen2 = 'simulation')
```

## SF_12_PCS

```{r}
sf12.p.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'SF_12_PCS')

plot_mean_comparison(pivoted.df = sf12.p.pivoted, 
                     var = 'SF_12_PCS', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

compare_boxplot_long(pivoted.df = sf12.p.pivoted,
                     var = 'SF_12_PCS',
                     scen1 = 'raw',
                     scen2 = 'simulation')
```

```{r}
sf12.p.t.tests <- two_sample_t_test(cv, 'cv', raw, 'raw', 'SF_12_PCS')
sf12.p.t.tests
```

```{r}
yearly_box_plots(pivoted.df = sf12.p.pivoted,
                 var = 'nutrition_quality',
                 scen1 = 'raw',
                 scen2 = 'simulation')
```

### 2023-05-16 minos/validation/handovers.Rmd
Renamed all instances of SF_12 to SF_12_MCS, and added the SF_12_PCS variable. Also created a PCS module, and tried to modify the outcome visualisation stuff but made some mistakes so still WIP. Handovers work, but cross-validation also still has some issues

```{r}
source('Minos/minos/validation/utils.r')
```

@@

out.path <- 'Minos/output/default_config/'
base.dat <- read_output(out.path, 'baseline')
```

## Constants

```{r}
start.year <- 2020

@@

## SF12

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12 <- rbind(raw.sf12, base.sf12)

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.2 <- rbind(raw.sf12.2, base.sf12.2)

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12 MCS)') +
  xlab('Year') +
  ylab('SF12')

ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)
```

>>>>

```{r}
source('Minos/minos/utils_datain.R')
```

```{r, include=FALSE}
start.year <- 2020

@@

out.path <- 'Minos/output/default_config/'
base.dat <- read_singular_local_out(out.path, 'baseline')
```

@@

## SF_12_MCS

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12.m <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.m <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12.m <- rbind(raw.sf12.m, base.sf12.m)

# Now plot
ggplot(data = sf12.m, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12_MCS)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12_MCS')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.m.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.m.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  filter(pidp %in% raw.sf12.m.wave1) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.m.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(SF_12_MCS > 0) %>%
  filter(pidp %in% raw.sf12.m.wave1) %>%
  group_by(time) %>%
  summarise(sf12.m = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.m.2 <- rbind(raw.sf12.m.2, base.sf12.m.2)

# Now plot
ggplot(data = sf12.m.2, mapping = aes(x = time, y = sf12.m, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12_MCS)') +
  xlab('Year') +
  ylab('SF12_MCS')

ggsave(filename = 'SF12_MCS_wav1.png',
       plot = last_plot(),
       path = save.path)
```

## SF_12_PCS

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12.p <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.p <- base.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12.p <- rbind(raw.sf12.p, base.sf12.p)

# Now plot
ggplot(data = sf12.p, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Wellbeing (SF12_PCS)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12_PCS')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.p.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.p.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  filter(pidp %in% raw.sf12.p.wave1) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.p.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(SF_12_PCS > 0) %>%
  filter(pidp %in% raw.sf12.p.wave1) %>%
  group_by(time) %>%
  summarise(sf12.p = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.p.2 <- rbind(raw.sf12.p.2, base.sf12.p.2)

# Now plot
ggplot(data = sf12.p.2, mapping = aes(x = time, y = sf12.p, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Wellbeing (SF12_PCS)') +
  xlab('Year') +
  ylab('SF12_PCS')

ggsave(filename = 'SF12_PCS_wav1.png',
       plot = last_plot(),
       path = save.path)
```
